{\Huge Introduction and Related work}

### 2017-12-13 paper/paper.tex
fixed paper

\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{chngcntr}
\usepackage{enumitem}
\usepackage[small]{titlesec}
\newlist{paragraphlist}{enumerate}{1}

@@

    A Bittorrent client application listen to a specific port in every machine. To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a ip address to the NAT. The UPNP is a way to configure the NAT in any programming language. Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.

@@

  \section*{Algorithms}
  \begin{flushleft}
    \textbf{Super Seeding} is a new seeding algorithm designed to help a torrent initiator with limited bandwidth "pump up" a large torrent, reducing the amount of data it needs to upload in order to spawn new seeds in the torrent.

@@

    When a seeding client enters "super-seed mode", it will not act as a standard seed, but masquerades as a normal client with no data. As clients connect, it will then inform them that it received a piece -- a piece that was never sent, or if all pieces were already sent, is very rare. This will induce the client to attempt to download only that piece.

@@

    This method has resulted in much higher seeding efficiencies, by both inducing peers into taking only the rarest data, reducing the amount of redundant data sent, and limiting the amount of data sent to peers which do not contribute to the swarm. Prior to this, a seed might have to upload 150% to 200% of the total size of a torrent before other clients became seeds. However, a large torrent seeded with a single client running in super-seed mode was able to do so after only uploading 105% of the data. This is 150-200% more efficient than when using a standard seed.

@@

    Super-seed mode is 'NOT recommended for general use. While it does assist in the wider distribution of rare data, because it limits the selection of pieces a client can downlad, it also limits the ability of those clients to download data for pieces they have already partially retrieved. Therefore, super-seed mode is only recommended for initial seeding servers.

@@

    When to enter end game mode is an area of discussion. Some clients enter end game when all pieces have been requested. Others wait until the number of blocks left is lower than the number of blocks in transit, and no more than 20. There seems to be agreement that it's a good idea to keep the number of pending blocks low (1 or 2 blocks) to minimize the overhead, and if you randomize the blocks requested, there's a lower chance of downloading duplicates.

    \textbf{Choking and optimistic Unchoking algorithm} - Choking is done for several reasons. TCP congestion control behaves very poorly when sending over many connections at once. Also, choking lets each peer use a tit-for-tat-ish algorithm to ensure that they get a consistent download rate.

    The choking algorithm described below is the currently deployed one. It is very important that all new algorithms work well both in a network consisting entirely of themselves and in a network consisting mostly of this one.

    There are several criteria a good choking algorithm should meet. It should cap the number of simultaneous uploads for good TCP performance. It should avoid choking and unchoking quickly, known as 'fibrillation'. It should reciprocate to peers who let it download. Finally, it should try out unused connections once in a while to find out if they might be better than the currently used ones, known as optimistic unchoking.

    The currently deployed choking algorithm avoids fibrillation by only changing choked peers once every ten seconds.

    Reciprocation and number of uploads capping is managed by unchoking the four peers which have the best upload rate and are interested. This maximizes the client's download rate. These four peers are referred to as downloaders, because they are interested in downloading from the client.

    Peers which have a better upload rate (as compared to the downloaders) but aren't interested get unchoked. If they become interested, the downloader with the worst upload rate gets choked. If a client has a complete file, it uses its upload rate rather than its download rate to decide which peers to unchoke.

    For optimistic unchoking, at any one time there is a single peer which is unchoked regardless of its upload rate (if interested, it counts as one of the four allowed downloaders). Which peer is optimistically unchoked rotates every 30 seconds. Newly connected peers are three times as likely to start as the current optimistic unchoke as anywhere else in the rotation. This gives them a decent chance of getting a complete piece to upload.

@@

  \section*{Our application}
  \begin{flushleft}

@@

  \end{flushleft}
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{chngcntr}
\usepackage{enumitem}
\usepackage[small]{titlesec}
\newlist{paragraphlist}{enumerate}{1}

@@

    A Bittorrent client application listen to a specific port in every machine. To be able to add this port to the NAT in it's router, one must use \textbf{universal plug in play (UPnP)} to avoid menually adding a port and a IP address to the NAT. The UPNP is a way to configure the NAT in any programming language. Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.

@@

  \section*{Algorithms}
  \begin{flushleft}
    \textbf{Super Seeding} is a new seeding algorithm designed to help a torrent initiator (The first seeder) with limited bandwidth to "pump up" a large torrent, reducing the amount of data it needs to upload in order to spawn new seeds in the torrent.

@@

    When a seeding client enters "super-seed mode", it does not act as a standard seed, but masquerades as a normal client with no data. As clients connect, it will then inform them that it received a piece -- a piece that was never sent, or if all pieces were already sent, is very rare. This will induce the client to attempt to download only that piece.

@@

    This method has resulted in much higher seeding efficiencies, by both inducing peers into taking only the rarest data, reducing the amount of redundant data sent, and limiting the amount of data sent to peers which do not contribute to the swarm. Prior to this, a seed might have to upload 150\% to 200\% of the total size of a torrent before other clients became seeds. However, a large torrent seeded with a single client running in super-seed mode was able to do so after only uploading 105\% of the data. This is 150-200\% more efficient than when using a standard seed.

@@

    Super-seed mode is 'NOT recommended for general use. While it does assist in the wider distribution of rare data, because it limits the selection of pieces a client can download, it also limits the ability of those clients to download data for pieces they have already partially retrieved. Therefore, super-seed mode is only recommended for initial seeding servers.

@@

    When to enter end game mode is an area of discussion. Some clients enter end game when all pieces have been requested. Others wait until the number of blocks left is lower than the number of blocks in transit, and no more than 20. There seems to be an agreement that it's a good idea to keep the number of pending blocks low (1 or 2 blocks) to minimize the overhead, and if you randomize the blocks requested, there's a lower chance of downloading duplicates.

@@

  \end{flushleft}
  \section*{Our application}
  \begin{flushleft}

@@

  \end{flushleft}
  \section*{Sources}
  \begin{flushleft}
    1. \href{http://www.rasterbar.com/products/libtorrent/udp_tracker_protocol.html}{udp tracker protocol}

    2. \href{https://wiki.theory.org/index.php/BitTorrentSpecification}{Bit Torrent Specification}
  \end{flushleft}
\end{document}
